Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm} \Large{Stagnating State Funding for Higher Education and its Effect on Faculty at Public Universities}

### 2023-12-23 text/sections/09-figures-tables.tex
Updates.

@@

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{State Funding and Total Professor Hiring at Public Universities, Total for 2011--2021.}
    \includegraphics[width=0.8\textwidth]{figures/hiring-correlation.png}
    \label{fig:hiring-correlation}
    \justify
    \footnotesize
    \textbf{Note}:
    This figure shows the correlation between state funding and the number of total number of professors hired at public universities between 2011--2021, and the line is an OLS line of best-fit.
    Data for the number of faculty hired at public universities are provided by \cite{wapman2022quantifying,wapman2022zenodo}, and funding data from IPEDS.
\end{figure}

>>>>

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{State Funding and Total Professor Hiring at Public Universities, Total for 2011--2021.}
    \includegraphics[width=0.8\textwidth]{figures/hiring-correlation.png}
    \label{fig:hiring-correlation}
    \justify
    \footnotesize
    \textbf{Note}:
    This figure shows the correlation between state funding and total number of professors hired at each public university between 2011--2021; the line is an OLS line of best-fit.
    Data for the number of faculty hired at public universities are provided by \cite{wapman2022quantifying,wapman2022zenodo}, and funding data from IPEDS.
\end{figure}

@@
